factor_explorer

### 2014-06-23 ijlyttle/factor_explorer.Rmd
adds color bands

```{r load_data}
sets <- c("item", "parent", "school", "scoredItem", "student")

@@

# there's a clever way to do this, but beyond me for naw
dict_item2012 <- fn_make_df(item2012dict) 
dict_parent2012 <- fn_make_df(parent2012dict) 
dict_school2012 <- fn_make_df(school2012dict) 
dict_scoredItem2012 <- fn_make_df(scoredItem2012dict) 
dict_student2012 <- fn_make_df(student2012dict)

@@

selectInput(
  "country",
  label = "Countries",
  choices = levels(student2012$CNT),
  selected = c("United States of America", "Canada"),
  multiple = TRUE
)

selectInput(
  "x_factor",
  label = "X-axis factor",
  choices = var_names_factor,
  selected = "ST04Q01"
)

selectInput(
  "fill_factor",
  label = "Fill factor",
  choices = var_names_factor,
  selected = "ST26Q03"
)
```

@@

renderPlot({
  ggplot(
    data = rct_data()
  ) + 
  geom_violin(
    aes_string(
      x = input$x_factor, 
      y = input$subject),
      scale = "width"
  ) + 
  geom_boxplot(
    aes_string(
      x = input$x_factor,
      y = input$subject,
      fill = input$fill_factor
    ),
    alpha = 0.75
  ) + 
#   geom_dotplot(
#     aes_string(
#       x = input$x_factor,
#       y = input$subject,
#       fill = input$fill_factor
#     ),
#     binaxis = "y", 
#     stackdir = "center", 
#     position = "dodge") + 
  facet_grid(CNT ~ .) + 
  scale_x_discrete(name = rct_labels()[["x"]]) +  
  scale_y_continuous(limits = c(0, 1000), name = rct_labels()[["y"]]) +
  scale_fill_brewer(type = "seq", name = rct_labels()[["fill"]]) 
})

renderPlot({
  ggplot(
    aes_string(
      x = input$x_factor,
      fill = input$fill_factor
    ),
    data = rct_data()
  ) +
  geom_bar(position = "dodge", color = "black") +   
  facet_grid(CNT ~ ., scales = "free_y") + 
  scale_x_discrete(name = rct_labels()[["x"]]) +  
  scale_y_continuous(name = "number of students") +
  scale_fill_brewer(type = "seq", name = rct_labels()[["fill"]]) 
})
```

>>>>

```{r load_data}
#sets <- c("item", "parent", "school", "scoredItem", "student")
sets <- "student"

@@

# there's a clever way to do this, but beyond me for naw
# dict_item2012 <- fn_make_df(item2012dict) 
# dict_parent2012 <- fn_make_df(parent2012dict) 
# dict_school2012 <- fn_make_df(school2012dict) 
# dict_scoredItem2012 <- fn_make_df(scoredItem2012dict) 
dict_student2012 <- fn_make_df(student2012dict)

@@

selectInput(
  "country",
  label = "Countries",
  choices = levels(student2012$CNT),
  selected = c("United States of America", "Peru", "China-Shanghai"),
  multiple = TRUE
)

selectInput(
  "x_factor",
  label = "X-axis factor",
  choices = var_names_factor,
  selected = "ST27Q03"
)

selectInput(
  "fill_factor",
  label = "Fill factor",
  choices = var_names_factor,
  selected = "ST28Q01"
)
```

@@

renderPlot({
  ggplot(
    data = rct_data()
  ) + 
  geom_rect(
    aes(fill = CNT),
    xmin = -Inf, xmax = Inf, 
    ymin = -Inf, ymax = Inf,
    alpha = 0.5,
    data = data.frame(CNT = unique(rct_data()$CNT))
  ) + 
  geom_violin(
    aes_string(
      x = input$x_factor, 
      y = input$subject),
      scale = "width"
  ) + 
#   geom_boxplot(
#     aes_string(
#       x = input$x_factor,
#       y = input$subject,
#       group = input$fill_factor
#     ),
#     fill = "white",
#     alpha = 1,
#   ) + 
  geom_boxplot(
    aes_string(
      x = input$x_factor,
      y = input$subject,
      alpha = input$fill_factor
    ),
    fill = "blue"
  ) + 
  facet_grid(CNT ~ .) + 
  scale_x_discrete(name = rct_labels()[["x"]]) +  
  scale_y_continuous(limits = c(0, 1000), name = rct_labels()[["y"]]) +
  scale_alpha_discrete(range = c(0.1, 0.9), na.value = 0, name = rct_labels()[["fill"]]) +  
  scale_fill_brewer(type = "seq", palette = "BuGn", guide = FALSE) 
})

renderPlot({
  ggplot(
    data = rct_data()
  ) +
  geom_rect(
    aes(fill = CNT),
    xmin = -Inf, xmax = Inf, 
    ymin = -Inf, ymax = Inf,
    alpha = 0.5,
    data = data.frame(CNT = unique(rct_data()$CNT))
  ) + 
  geom_bar(
    aes_string(
      x = input$x_factor,
      group = input$fill_factor
    ),
    position = "dodge", 
    fill = "white", 
    alpha = 1,
    color = "black"
  ) +   
  geom_bar(
    aes_string(
      x = input$x_factor,
      alpha = input$fill_factor
    ),
    position = "dodge", 
    fill = "blue"
  ) +   
  facet_grid(CNT ~ ., scales = "free_y") + 
  scale_x_discrete(name = rct_labels()[["x"]]) +  
  scale_y_continuous(name = "number of students") +
  scale_alpha_discrete(range = c(0.1, 0.9), na.value = 0, name = rct_labels()[["fill"]]) +  
  scale_fill_brewer(type = "seq", palette = "BuGn", guide = FALSE) 
})
```
